---
title: 'Homework #???'
author: "Your Name Here"
date: "Month Day, Year"
output: html_document
---

This example assignment examines the `Hitters` dataset in the `ISLR` package.  To begin, make sure the `ISLR` package is installed and run the following code:
```{r}
library(ISLR)
```

### Question 1
Calculate the following descriptive statistics:

a) What is the mean number of hits?
```{r}
mean(Hitters$Hits)
```

b) What is the standard deviation of the number of hits?
```{r}
sd(Hitters$Hits)
```


### Question 2
Create and interpret the following plots:

a) A histogram for the number of home runs.
```{r, fig.height = 3, fig.width = 3, fig.align = "center"}
hist(Hitters$HmRun, xlab = "Home Runs", main = "Histogram of Home Runs")
```

The number of home runs is not symmetric as most hitters had a small number of home runs (skewed right).

b) A scatter plot showing the number of home runs on the horizontal axis and the number of runs on the vertical axis.
```{r, fig.height = 3, fig.width = 3, fig.align = "center"}
plot(Hitters$HmRun, Hitters$Runs, xlab = "Home Runs", ylab = "Runs")
```

It looks like there is a positive relationship between the number of home runs and number of runs.
